Maintenance planning on French military aircraft operations

### 2018-09-19 R/presentations/CLAIO_presentation/presentation.Rmd
second version of CLAIO ppt

## Model: time consumption

@@

\begin{align}
 & u_{it} \geq \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j 
    & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage1}\\
 & u_{it} \geq u^{min} (1 - \sum_{t' \in \mathcal{T}^{s}_t} m_{it'})
    & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage2}\\
 & u_{it} \in [0, \max_j{\{H_j\}}]
    & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage_lower}\\
 & rut_{it} \leq rut_{i(t-1)} + H^{M} m_{it} - u_{it}
    & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\
 & rut_{i0} = Rut^{Init}_i
       & i \in \mathcal{I} \label{eq:rut_initial}\\
 & rut_{it} \geq H^{M} m_{it'}
        & t \in \mathcal{T}, t' \in \mathcal{T}^{s}_t, i \in \mathcal{I}\label{eq:rut_lower}\\
 & rut_{it} \in [0,H^{M}]
        & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu}
\end{align}

@@

* Cluster availability.
* Minimum duration for task assignment.

@@

Instances have been generated with the following main characteristics:

@@

* Small instances have **30.000 variables** and **20.000 constraints**.
* Medium instances have **80.000 variables** and **50.000 constraints**.
* Runs of 30 minutes have been done on 30 randomly generated cases per scenario and they return a gap between 20% and 40% if a solution exists.
* CPLEX was used in an i7, quadcore Ubuntu 18.04 workstation.

@@

* `r infeasible[1]`% of instances were proved infeasible inmediately.
* From feasible small instances, a gap of `r scen_means[1]`% was found after 30 min
* From feasible medium instances, a gap of `r scen_means[2]`% was found after 30 min.

@@

* More extreme (bigger) scenarios need to be tested: more tasks and more resources.
* A deeper analysis on the detailed solving process is envisioned. Including extending the solving time.
* Benchmarking of solvers (gurobi, CBC, choco and CPO) is work in progress. Also: heuristics.
* The inclusion of new possibilities, such as the planned storage of resources is pending.
* A stochastic sensibility analysis needs to be done, including taking account of stochasticity in the input data.

>>>>

<!-- ## Model: time consumption -->

@@

<!-- \begin{align} -->
<!--  & u_{it} \geq \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j  -->
<!--     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage1}\\ -->
<!--  & u_{it} \geq u^{min} (1 - \sum_{t' \in \mathcal{T}^{s}_t} m_{it'}) -->
<!--     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage2}\\ -->
<!--  & u_{it} \in [0, \max_j{\{H_j\}}] -->
<!--     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:usage_lower}\\ -->
<!--  & rut_{it} \leq rut_{i(t-1)} + H^{M} m_{it} - u_{it} -->
<!--     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\ -->
<!--  & rut_{i0} = Rut^{Init}_i -->
<!--        & i \in \mathcal{I} \label{eq:rut_initial}\\ -->
<!--  & rut_{it} \geq H^{M} m_{it'} -->
<!--         & t \in \mathcal{T}, t' \in \mathcal{T}^{s}_t, i \in \mathcal{I}\label{eq:rut_lower}\\ -->
<!--  & rut_{it} \in [0,H^{M}] -->
<!--         & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu} -->
<!-- \end{align} -->

@@

* Minimum cluster availability.
* Minimum duration for task assignment.
* Hour consumption of resources depending on tasks and maintenances.

@@

@@

* Small instances have **30.000 variables** and **20.000 constraints**.
* Medium instances have **80.000 variables** and **50.000 constraints**.
* Runs of 30 minutes have been done on 30 randomly generated cases per scenario.
* CPLEX was used in an i7, quadcore Ubuntu 18.04 workstation.

@@

* `r infeasible[1]`% of instances were proved infeasible inmediately.
* From feasible small instances, a mean gap of `r scen_means[1]`% was found after 30 min.
* From feasible medium instances, a mean gap of `r scen_means[2]`% was found after 30 min.

@@

* More extreme (bigger) scenarios: more tasks and more resources.
* A deeper analysis on the detailed solving process.
* Benchmarking of solvers (gurobi, CBC, choco and CPO).
* Heuristics for large scale instances.
* The inclusion of new possibilities, such as the planned storage of resources.
* A stochastic sensibility analysis, including taking account of stochasticity in the input data.
